The Psychology of Online Political Hostility -- How Aggressiveness of People Effects Their Online and Offline Comment Towards Political Incidents

### 2024-02-13 main_folder/paper/The Psychology of Online Political Hostility – How Aggressiveness of People Effects Their Online and Offline Comment Towards Political Incidents.qmd
llm

# Discussion
(what did we learn from this study?)

>>>>

# Discussion

Our analysis reveals a positive correlation between individuals' levels of aggression and the degree of hostility they exhibit in both online and offline political discussions. This suggests that individuals with higher aggression tend to display more pronounced political hostility regardless of the medium. While the original paper focused on the impact of status-driven risk-taking on online versus offline hostility, finding a positive correlation, our study extends this understanding by demonstrating that the dimension of aggression plays a similar role, highlighting the significant influence of personal traits on political hostility in both platforms.

Contrary to our initial hypothesis that individuals with aggressive personalities would exhibit more different behaviors in online versus offline political discussions, our data did not show a correlation between aggression levels and the difference in hostility between these two contexts. This finding diverges from our expectations and suggests that, despite the increased anonymity and lack of accountability online, aggression does not significantly alter the perceived severity of political conflicts between online and offline environments. This is in line with the original paper's suggestion that political conflicts are not perceived to be more severe online than offline, indicating that individuals with aggressive traits do not differ markedly from average participants in their perception of hostility severity across these platforms.

In summary, our replication study reveals that individual aggressiveness correlates with increased political hostility, uniformly affecting both online and offline discussions. Crucially, it also indicates that there is not a significant correlation between aggression levels and the difference in hostility between these two contexts even for the more aggressive Internet users. This finding challenges the premise that digital environments inherently amplify political antagonism, instead highlighting the overarching role of inherent personal traits in dictating the tone of political discourse, irrespective of the medium.
